A Systematic Literature Review on Extensions to Role Based Access Control

### 2013-03-04 paper/sections/process.tex
Adds elimination totals.

The result set size stopping criteria was chosen due to a technical limitation of some search engines.  The stopping criteria related to the last ten titles is meant to stop after relevant results are no longer being returned by the search engine.  After gathering all 12 data sets, the authors combined the papers into a master list by systematically comparing the bibliographic information for each.  The master list of 1716 papers was used to perform a series of elimination rounds to narrow the list of papers and identify primary sources.

@@

The first round of elimination was performed by strict examination of the title.  Each researcher was tasked with deciding on elimination by answering the following questions:

@@

>>>>

The result set size stopping criteria was chosen due to a technical limitation of some search engines.  The stopping criteria related to the last ten titles is meant to stop after relevant results are no longer being returned by the search engine.  After gathering all 12 data sets, the authors combined the papers into a master list by systematically comparing the bibliographic information for each.  The master list of 1716 papers was used to perform a series of elimination rounds to narrow the list of papers and identify primary sources.  Table \ref{tab:eliminations} shows the total number of papers selected by each author for each round and how many papers from the disjoint set for each round survived to the next round.

@@

The first round of elimination was performed by strict examination based on the title.  Each author was tasked with deciding on elimination by answering the following questions:

@@

\begin{table}
\centering
\begin{tabular}{ c c | c | c | c | }
\cline{3-5}

 & \multicolumn{1}{ c| }{} & \textbf{Title} & \textbf{Abstract} & \textbf{Paper Body} \\ \hline

\multicolumn{1}{ |c| }{Eric}  &  & 305 & 86 & 46 \\ \hline
\multicolumn{1}{ |c| }{Hwang} &  & 176 & 102 & 42 \\ \hline

\multicolumn{1}{ c| }{} & Overlap & 249 & 51 & 24 \\ \cline{2-5}
\multicolumn{1}{ c| }{} & Disjoint & 232 & 137 & 64 \\ \cline{2-5}
\multicolumn{1}{ c| }{} & Rejected & 208 & 116 & 59 \\ \cline{2-5}
\multicolumn{1}{ c| }{} & Retained & 41 & 21 & 5 \\ \cline{2-5}
\multicolumn{1}{ c| }{} & \textbf{Total} & 290 & 72 & 29 \\ \cline{2-5}

\end{tabular}
\caption{Elimination Rounds}
\label{tab:search_results}
\end{table}
